CRUSE to Safe Cycling in Ireland

### 2023-10-03 paper.qmd
Add scenarios, close #12

# # Uncomment for draft versions:
format: 
  html: default
  docx: default
# Uncomment for formatted version
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
# #   # pdf: default

@@

::: {#fig-route-types layout-nrow="2"}

![](images/paste-5.png)

@@

Illustration of the Fastest and Quietest route networks for central and East Limmerick.

@@

The datasets outlined above were used to generate estimates of cycling currently (the 'Baseline' scenario) and under four scenarios of cycling potential: Near Market, Climate Action Plan, Go Dutch, and Ebike.
Each of these scenarios is described below.
<!-- TODO: add table. -->

@@

@@

An illustration of the level of cycling under various scenarios in the county of Limerick is shown in Figure \@ref(fig:distance-frequency).
The results will vary from county to county.

 Climate Action Plan Go Dutch Ebike

>>>>

# # Uncomment for draft versions:
format: 
  html: default
  docx: default
# # Uncomment for formatted version
#   elsevier-pdf:
#     keep-tex: true
#     journal:
#       name: Journal Name
#       formatting: preprint
#       model: 3p
#       cite-style: super
# # #   # pdf: default

@@

::: {#fig-route-types layout-nrow="2"}
![](images/paste-5.png)

@@

Illustration of the Fastest and Quietest route networks for central and East Limmerick.
:::

The datasets outlined above were used to generate estimates of cycling currently (the 'Baseline' scenario) and under four scenarios of cycling potential: Near Market, Climate Action Plan, Go Dutch, and Ebike.
Each of these scenarios is described below, as illustrated in Figure @fig-scenarios.
<!-- TODO: add table. -->

::: {#fig-scenarios}

![](images/paste-7.png)

Distance-mode share graph for Limerick used to communicate the different scenarios. Source: county level view for Limerick in the open access CRUSE Tool at <https://cruse.bike/limerick>.

@@

### Baseline

@@

### Near Market

@@

### Climate Action Plan

The Climate Action Plan scenario is loosely based on the Irish Government's [Climate Action Plan 2021](https://www.gov.ie/en/publication/6223e-climate-action-plan-2021/), which contains policies for action to achieve a 51% reduction in overall greenhouse gas emissions by 2030, on a path towards net-zero by 2050.
For transport, this includes 500,000 extra walking, cycling and public transport trips per day by 2030.
In terms of car travel, the target is to "Increas[e] the proportion of kilometres driven by passenger electric cars to between 40 and 45% by 2030, in addition to a reduction of 10% in kilometres driven by the remaining internal combustion engine cars."
This equates to a 5.5 to 6% reduction in total car km driven.

To model this decrease in car driver km, cycling uptake increases in line with the Go Dutch scenario.
However, we only model shift from driving to cycling.
There is no shift from other modes of transport to cycling.

### Go Dutch

Under the Go Dutch scenario cycling reaches levels equivalent to those found in the Netherlands, taking account of the effects of route hilliness (measured as mean gradient) and route distance.
This scenario uses the same model that was used PCT, allowing trips to shift from any other mode to cycling [@lovelace2017].

## Ebike

Also based on the PCT scenario with the same name, the Eike scenario in CRUSE takes Go Dutch cycling uptake, and adds onto this the impact of increased ebike usage, which allows for longer cycle trips.
However, travel to primary and secondary schools still uses Go Dutch uptake, since no ebike scenario has been developed for school journeys, and children may be less likely to own ebikes than adults.
